Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-01 snapshot_system/failover.tex
Updated terminology in plots.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. Links to a Block},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a block in the global index}
  \label{fig-vo-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Container links},
		xlabel={Number of VMs},
		ylabel={Avgerage Container links},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=ContainerLinks] {figures/vo_container_links.txt};
		%\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a container in the global index (for VO)}
  \label{fig-vo-container-links}
\end{figure}

@@

in our current testbed we have measured the average number of links
per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-container-links})
in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
was 11 using a 5\% CDS. From Figure~\ref{vo-container-links} you can see that as you add VMs, the average
number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
should continue to increase at a slower rate. 
For the VC model, we have to consider both CDS chunks and 
Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
}

>>>>

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig-vo-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Container links},
		xlabel={Number of VMs},
		ylabel={Avg. links to an FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		%\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB Filesystem Block in the global index (for VO)}
  \label{fig-vo-fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Avg CDS Container Links},
		xlabel={Number of VMs},
		ylabel={Avg. links to CDS FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
		%\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB CDS Filesystem Block for (VC with 5\% CDS)}
  \label{fig-cds-fsb-links}
\end{figure}

@@

in our current testbed we have measured the average number of links
per block (Figure~\ref{vo-links}) and number of links per chunk (Figure~\ref{vo-fsb-links})
in our dataset. For the complete dataset, we also found the average number of links to CDS chunks, which
was 11 using a 5\% CDS. From Figure~\ref{vo-fsb-links} you can see that as you add VMs, the average
number of links to a chunk increases. We expect that this trend will level out with larger datasets, but
should continue to increase at a slower rate. 
For the VC model, we have to consider both CDS chunks and 
Non-CDS chunks. In the VO model all data is shared, but in VC only the CDS data is shared, but at a much
higher rate. This gives a strong advantage to VC, in that for a large percent of the data (95-99\%), there
is only one VM pointing to each Non-CDS chunk. You can see the increase in reliability in Figure~\ref{fig-vm-availability}.
}
